\section{Conclusions and Future Work}
\label{sec:conclusion}
 \vspace{-.6cm}
We have presented a technique for the construction of
domain-specific model editors in MPS, where these editors are based on
a set of composed DSLs and on a description of the process that
should be followed when building the models for that domain. We have applied our
approach to the construction of an editor for gathering software requirements
at two levels: firstly, we build an abstract requirements gathering framework,
following the guidelines in the MIRA framework~\cite{MIRA13}; secondly, we
specialize that framework for our industrial partners at Diehl, by introducing
a specific requirements refinement process for controllers for cooling systems.

The main technical contribution of this paper are the means to define a process
to assist in building a model in a domain-specific model-driven development
framework. This process is based on a set of model analyses running in the
background of the framework and can guide the user until the model is complete.
At a methodological level, our contribution regards our ideas on the separation
of the \emph{framework customizer} and the  \emph{domain specific tool
developer} roles. While the former is responsible for defining a number of
fundamental ``brick'' DSLs, the latter further specializes them for a particular
application by potentially adding more languages and organizing the whole
according to a process.

In its current state, the main shortcoming of the technique we propose in this
paper is the fact that it is the complete responsibility of the domain-specific
tool developer to check the consistency of the properties being checked during
the unfolding of the process, as well as their logical sequence in the process.
Additional assistance during this step could be envisaged, for example in the
form of automated checks for logical inconsistencies in the conditions that
define each state in the process. Also, arbitrary deletions in the model may
lead to inconsistencies in the current state of edition in the dashboard. A
carefully designed process may avoid such inconsistencies, although automated
help for the tool developer would also be important here. Finally, scalability
is also an issue as analyses currently run very often in the background,
which will rapidly lead to performance degradation in larger systems. Potential
solutions to this problem are currently being investigated by colleagues of our
at fortiss~\cite{Models17Sudeep}.

As future work, beyond mitigating the shortcomings identified above, we will
work continue working with Diehl Aerospace to further develop the case study we
present in this paper into a usable requirements gathering system. Other partner companies
have shown interest in applying the work we present to domains other than
requirements engineering, which means in the future building or assembling
different language stacks as well as different processes. Closer integration
with MPS is necessary in order to perform analyses in the background only when
strictly needed. Finally, mechanisms for the systematic creation of standalone
editors that implement process-aware model-driven development environments
is also in our future plans.
 \vspace{-.6cm}
